---
title: "Josh Analysis"
author: "jschoenbachler"
date: "2021-12-16"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

## Introduction

All data files are located within the `data` folder. The data consist of movie titles, their availability on streaming platforms (Netflix, Prime Video, Hulu, and Disney+).

The source can be found [here](https://www.kaggle.com/ruchi798/movies-on-netflix-prime-video-hulu-and-disney).

## Load data

Load data example here.

```{r load libraries}
library(data.table)
library(ggplot2)
```

Read data, filter to last 50 years, and add service column
```{r load all data}
movieDT = fread('data/MoviesOnStreamingPlatforms_updated.csv')
movieDT = movieDT[,-c('V1')]
movieDT = movieDT[Year >= 1971,]
movieDT[, service := ""]
movieDT[Netflix == 1, service := "Netflix"]
movieDT[Hulu == 1, service := "Hulu"]
movieDT[`Prime Video` == 1, service := "Prime Video"]
movieDT[`Disney+` == 1, service := "Disney+"]
movieDT[(Netflix + Hulu + `Prime Video` + `Disney+`) > 1, service := "Multiple"]
```

## Extract numeric values from IMDb and Rotten Tomatoes
```{r}
movieDT[, imdb_num := as.numeric(
  gsub(pattern="\\/(.*)", replacement="", IMDb, perl = TRUE))]

movieDT[, tomatoe_num := as.numeric(
  gsub(pattern="\\/(.*)", replacement="", `Rotten Tomatoes`, perl = TRUE))]
``` 
## Plots
### Number of movies in each streaming service by decade
```{r}
ggplot(movieDT, aes(x = Year, fill = service)) + geom_bar(stat="bin", binwidth = 10)
```

### Number of movies in each streaming service by IMDB score
```{r}
ggplot(movieDT, aes(x = imdb_num, fill = service)) + geom_bar(stat="bin", binwidth = 1.0)
```

### Number of movies in each streaming service by Rotten Tomatoes Score
```{r}
ggplot(movieDT, aes(x = tomatoe_num, fill = service)) + geom_bar(stat="bin", binwidth = 10)
```

