---
title: "Sample Analysis"
author: "jschoenbachler & arefnel"
date: "2020-12-16"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

## Introduction

All data files are located within the `data` folder. The data consist of movie titles, their availability on streaming platforms (Netflix, Prime Video, Hulu, and Disney+).

The source can be found [here](https://www.kaggle.com/ruchi798/movies-on-netflix-prime-video-hulu-and-disney).

## Load data

Load data example here.

```{r load libraries}
library(data.table)
library(ggplot2)
```


```{r load all data}
movieDT = fread('data/MoviesOnStreamingPlatforms_updated.csv')
movieDT = movieDT[,-c('V1')]
head(movieDT, 5)
```

## extract numeric values from IMDb and Rotten Tomatoes
```{r}
movieDT[, imdb_num := as.numeric(
  gsub(pattern="\\/(.*)", replacement="", IMDb, perl = TRUE))]

movieDT[, tomatoe_num := as.numeric(
  gsub(pattern="\\/(.*)", replacement="", `Rotten Tomatoes`, perl = TRUE))]
``` 


## sample analysis
distribution of the year movies were made in for each streaming platform
```{r}
dt = melt(movieDT[,c('ID', 'Year', 'Netflix', 'Hulu', 'Prime Video', 'Disney+')],
          id.vars = c('ID', 'Year'), variable.name='stream_platform')
dt = dt[value==1][,-c('value')]

ggplot(dt) + geom_density(aes(x=Year, fill=stream_platform), bw=0.5) + 
  facet_wrap(~stream_platform, ncol=1) + 
  labs(title = 'year distribution vs. streaming  platform')
```

